%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Modified by: Dulshani Gunawardhana
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://dshgna.github.io/}{\Large Dulshani Gunawardhana}} & \href{mailto:degunawardhana@gmail.com}{degunawardhana@gmail.com}\\
  \href{http://dshgna.github.io}{http://dshgna.github.io}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {London School of Economics and Political Science}{London, UK}
      {MSc in Applied Social Data Science}{Sep 2020 - Sep 2021}
      \resumeItemListStart
	      \resumeItem{'We don't talk Anymore?'\textit{(Dissertation, Ongoing)}}
	      {When does polarization reach the tipping point that renders discussion infeasible? I explore this question by combining Artificial Intelligence and political science to compare Reddit's r/ChangeMyView against polarized subreddits. \textit{(Topic Modelling, Ideological Scaling, Deep Learning, Affective Polarization, Homophily, Python)}}
	      \resumeItem{Petitions in a Pandemic}
	      {How did the public mobilize the UK Government's e-petitioning system during the pandemic? What issues did they deem the most important? \textit{(Latent Dietrich Allocation, Model Evaluation, Python)}}
	      \resumeItem{Coursework}
	      {Machine Learning, Quantitative Text Analysis, Applied Regression Analysis, Causal Inference for Observational and Experimental Studies, Social Research Methods, Managing and Visualizing Data}
      \resumeItemListEnd
    \resumeSubheading
      {University of Moratuwa}{Sri Lanka}
      {BSc in Information Technology;  GPA: 3.73 (3.92/4.2)}{Jul 2010 - Dec 2014}
      \resumeItemListStart
	      \resumeItem{Awards}
	      {Gold Medal for Academic Excellence \textit{(Highest cumulative GPA from a class of 100)}}
      \resumeItem{Relevant Coursework}
      {Probability and Statistics, Advanced Topics in Mathematics \textit{(included Linear Algebra and Calculus)}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
 {Center for Care Policy and Evaluation, London School of Economics}{London, UK}
 {Research Assistant - Data Science}{Dec 2020 - Present}
 \resumeItemListStart
 \resumeItem{Assessment of COVID-19 policy responses for Adult Social Care}
{Created reports and visualization to aid the reporting and response for adult social care in the UK. \textit{(R, Python)}}
\resumeItem{Natural Language Processing (Ongoing)}
{Application of natural language processing techniques on documentation to assess the quality of adult social care in the UK.}
 \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Facebook}{Dublin, Ireland}
      {Project Manager - Hate Speech}{Mar 2019 - Sep 2020}
      \resumeItemListStart
        \resumeItem{Operations Analysis}
          {Deep dive investigation into the performance of operational metrics in global workflows, surfacing key business insights that were prioritized for roadmaps. \textit{(SQL)}}
        \resumeItem{Reporting}
          {Created weekly reports on operational metrics for senior leadership.}
        \resumeItem{Dashboards}
          {Created and maintained multiple dashboards for the designation of abusive keywords and analysing labelling experiments.\textit{(SQL, internal dashboarding tools)}}
        \resumeItem{Project Management and Policy Development}
      {Achieved a 2\% improvement of the hate speech accuracy metric (H2 2019) by leading several projects in policy refinement and process improvement.}
      \resumeItemListEnd

\resumeSubSubheading
      {Market Specialist - Sri Lanka}{May 2016 - Feb 2019}
      \resumeItemListStart
        \resumeItem{Market Operations}
          {Owned the end-to-end launch of vendor support for Sri Lanka, including operational ownership, policy guidance, quality measurement and onsite training.}
        \resumeItem{Market Expertise}
          {Provided expertise on the socio-political landscape of Sri Lanka in the efforts to curb ethnic tension and misinformation in the country.} 
          \resumeItem{Data Reporting and Automation}
          {Ideated and collaborated with CO Tooling to introduce an automated process for workflow creation resulting in the process being reduced from 16 hours to 20 minutes.\textit{(SQL, VBA)}}
      \resumeItemListEnd

    \resumeSubheading
      {Virtusa}{Colombo, Sri Lanka}
      {Software Engineer}{Jan 2015 - Dec 2015}
      \resumeItemListStart
        \resumeItem{Web Development}
          {Developed the front-end web interface and data retrieval for a web-based application for security investigations.\textit{(Java, Javascript)}}
        \resumeItem{Automated Testing}
             {Automated quality testing to ensure functional correctness of web components and optimal user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
 % \resumeSubHeadingListStart
  %  \resumeSubItem{QuantSoftware Toolkit}
     % {Open source python library for financial data analysis and machine learning for finance.}
    %\resumeSubItem{Github Visualization}
      %{Data Visualization of Git Log data using D3 to analyze project trends over time.}
 %   \resumeSubItem{Recommendation System}
  %    {Music and Movie recommender systems using collaborative filtering on public datasets.}
   % \resumeSubItem{Mac Setup}
   %   {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  %\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
